Automated Topic Naming

### 2012-01-20 ese/ese.tex
minor edit

We primarily relied on ROC (the area under the receiver operating
characteristic curve), as our measurement to compare the effectiveness
of semi-supervised and supervised learners. ROC is less biased than
F-Measure in cross-folds
validation~\cite{flach-icml03,Forman:2010:ACS:1882471.1882479} in the
case of class imbalance. We
feel that the fixed point of $0.5$ for random results allows us to
better describe the predictability achieved by some of these
techniques against random and ZeroR learners. 
We also include
F-Measure results to allow for the reader to validate against
F-Measure if they are more comfortable with it. Thus because of
F-Measure biased handling of class-imbalance and the inherent
class-imbalance that our data suffers from we chose ROC.

>>>>

We primarily relied on ROC (the area under the receiver operating
characteristic curve), as our measurement to compare the effectiveness
of semi-unsupervised and supervised learners. ROC is less biased than
F-Measure in cross-folds
validation~\cite{flach-icml03,Forman:2010:ACS:1882471.1882479} in the
case of class imbalance. We
feel that the fixed point of $0.5$ for random results allows us to
better describe the predictability achieved by some of these
techniques against random and ZeroR learners. 
We also include
F-Measure results to allow for the reader to validate against
F-Measure if they are more comfortable with it. Thus because of
F-Measure biased handling of class-imbalance and the inherent
class-imbalance that our data suffers from we chose ROC.
